Compositional equivalences based on Open pNets

### 2020-03-11 2016-Weak-FH-Bisim/WeakBisim.tex

  \medskip
  Checking that $\mathcal{R}$ is a weak FH-Bisimulation means checking, for each of these triples, that each WOT of one the states corresponds to a set of WOTs of the other, using the conditions from Definition \ref{def-Weak-bisim}.
  We give here two examples.

  \medskip
  Consider the first triple from the table, and transition $WS_3(n)$ from state $b0$ for some fixed integer $n$. Its easy to guess that it will correspond to $WI_3(n)$ of $000$.

  $ WS_3(n) = \openrule
  {\{\texttt{P}\mapsto \texttt{p-send(m1)}\}, True,
    (\texttt{b1\_msg}\gets \texttt{m1}, \texttt{b1\_ec}\gets n)}
  {000 \OTWeakarrow {\underline{\texttt{in(m1)}}} 100}
  $

$ WI_3(n) = \openrule
  {\{\texttt{P}\mapsto \texttt{p-send(m2)}\}, True,
    (\texttt{s1\_msg}\gets \texttt{m2}, \texttt{s1\_ec}\gets n)}
  {000 \OTWeakarrow {\underline{\texttt{in(m2)}}} 100}
  $

@@

\begin{itemize}
  \item Their sets of active (non-silent) holes is the same: $\{P\}$.
  \item Triple ($b1,  100,  \texttt{b1\_msg = s1\_msg} \land \texttt{b1\_ec = s1\_ec}$) is in $\mathcal{R}$.
  \item The verification condition \\
    $\forall fv_{OT}. \{ \Pred \land \Pred_{OT}\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}\!
   \left[\exists fv_{OT_x}.
  \left( \forall j\in J_x. \vis{\beta_j}\!=\!\gamma_{jx}\! \land\! \Pred_{OT_x}
     \!\land\! \alpha\!=\!\alpha_x\! \land\!  
     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)\right]\}}$

@@

$\forall m1. \{True \land True\hspace{3mm} \implies
\exists m2. \\
(\texttt{p-send(m1)} = \texttt{p-send(m2)}
\land True
\land \underline{\texttt{in(m1)}} = \underline{\texttt{in(m2)}}\\
\land (\texttt{b1\_msg = s1\_msg} \land \texttt{b1\_ec = s1\_ec})
\subst{(\texttt{b1\_msg}\gets \texttt{m}, \texttt{b1\_ec}\gets n)
  \uplus (\texttt{s1\_msg}\gets \texttt{m}, \texttt{s1\_ec}\gets n)})\}
$

@@

$\forall \texttt{m1}. \exists \texttt{m2}.
(\texttt{p-send(m1)} = \texttt{p-send(m2)}
\land \texttt{in(m1)} = \texttt{in(m2)}
\land \texttt{m1}=\texttt{m2} \land n=n)$

@@

  \bigskip
  Now consider the $3^{rd}$ triple from the table, and transition $WI_{8'}(n)$ from state $100$ to state $000$ for some fixed integer $n$. It should correspond to $WS_7(n)$ of $b1$.

  $ WI_{8'}(n) = \openrule
         {\{\texttt{Q}\mapsto \texttt{q-recv(s1-msg,s1-ec+n)}\}, True, ()}
         {100 \OTWeakarrow {\underline{\texttt{out(s1-msg,s1-ec+n)}}} 000}
         \ \forall n\ge 0$

  $ WS_7(n) = \openrule
         {\{\texttt{Q}\mapsto \texttt{q-recv(msg,ec+n)}\subst{ec\gets ec+n}\}, True, (ec\gets ec+n)}
         {b1 \OTWeakarrow {\underline{\texttt{out(msg,ec)}\subst{ec\gets ec+n}}} b0}
         \ \forall n\ge
         $

  \medskip       A similar reasonning gives us:

>>>>

  \medskip
  Checking that $\mathcal{R}$ is a weak FH-Bisimulation means checking, for each of these triples, that each (strong) OT of one the states corresponds to a set of WOTs of the other, using the conditions from Definition \ref{def-Weak-bisim}.
  We give here two examples.

  \medskip
  Consider the second triple from the table, and transition $SS_3$ from state $b0$. Its easy to guess that it will correspond to $WI_3(0)$ of $202$.

  $ SS_3 = \openrule
  {\{\texttt{P}\mapsto \texttt{p-send(m1)}\}, True,
    (\texttt{b1\_msg}\gets \texttt{m1}, \texttt{b1\_ec}\gets 0)}
  {b0 \OTWeakarrow {\underline{\texttt{in(m1)}}} b1}
  $

$ WI_3(0) = \openrule
  {\{\texttt{P}\mapsto \texttt{p-send(m2)}\}, True,
    (\texttt{s1\_msg}\gets \texttt{m2}, \texttt{s1\_ec}\gets 0)}
  {202 \OTWeakarrow {\underline{\texttt{in(m2)}}} 100}
  $

@@

\begin{itemize}
  \item Their sets of active (non-silent) holes is the same: $J' = J_x = \{P\}$.
  \item Triple ($b1,  100,  \texttt{b1\_msg = s1\_msg} \land \texttt{b1\_ec = s1\_ec}$) is in $\mathcal{R}$.
  \item The verification condition \\
    $\forall fv_{OT}. \{ \Pred \land \Pred_{OT}\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}\!
   \left[\exists fv_{OT_x}.
  \left( \forall j\in J_x. \vis{\beta_j}\!=\!\gamma_{jx}\! \land\! \Pred_{OT_x}
     \!\land\! \alpha\!=\!\alpha_x\! \land\!  
     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)\right]\}}$

@@

$\forall m1. \{True \land True\hspace{3mm} \implies
\exists m2. \\
(\texttt{[p-send(m1)]} = \texttt{[p-send(m2)]}
\land True
\land \underline{\texttt{in(m1)}} = \underline{\texttt{in(m2)}}\\
\land (\texttt{b1\_msg = s1\_msg} \land \texttt{b1\_ec = s1\_ec})
\subst{(\texttt{b1\_msg}\gets \texttt{m}, \texttt{b1\_ec}\gets 0)
  \uplus (\texttt{s1\_msg}\gets \texttt{m}, \texttt{s1\_ec}\gets 0)})\}
$

@@

$\forall \texttt{m1}. \exists \texttt{m2}.
(\texttt{p-send(m1)} = \texttt{p-send(m2)}
\land \texttt{in(m1)} = \texttt{in(m2)}
\land \texttt{m1}=\texttt{m2} \land 0=0)$

@@

  \bigskip
  Now consider the $3^{rd}$ triple from the table, and transition $SI_{4}$ from state $100$ to state $210$. It should correspond to $WS_4(0)$ of $b1$, where:

  $ SI_{4} = \openrule
         {\{\}, True, (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}, \texttt{s2\_ec}\gets \texttt{s1\_ec})}
         {100 \OTWeakarrow {\tau} 210}
         $

  $ WS_4(n) = \openrule
         {\{\}, True, (b1\_ec\gets b1\_ec+n)}
         {b1 \OTWeakarrow {\tau} b1}
         \ \forall n\ge 0
         $

  \medskip       A similar reasonning gives us\TODO{refaire}
